---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r }

```

```{r setwd}
setwd("C:/Users/Tanki/RepData_PeerAssessment1")
```
## Loading and preprocessing the data
```{r loaddata}
data <- read.csv("activity.csv")
library(dplyr)
library(ggplot2)
library(Hmisc)
```


## What is mean total number of steps taken per day?
```{r }
total_steps <- tapply(data$steps, data$date, sum, na.rm=TRUE)
hist(total_steps, col = "green", 
     breaks = 20,
     main = "Total number of steps taken each day",
     xlab = "Number of steps per day")
mean(total_steps,na.rm = TRUE)
median(total_steps,na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r }

by_interval<-group_by(data,interval)
avg<- summarise(by_interval,average=mean(steps,na.rm=TRUE))
ggplot(data=avg, aes(x=interval, y=average)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("average number of steps taken")

```
##On average across all the days in the dataset, the 5-minute interval contains the maximum number of steps?
```{r }
avg[which.max(avg$average),1]
```

## Imputing missing values
```{r }
na<-length(which(is.na(data$steps)))
print(paste("Total Na values ", na) )
```

##Replacing missing values, creating new dataset and creating Histogram
```{r }
data_filled <- data
data_filled$steps <- impute(data$steps, fun=mean)

total_steps1 <- tapply(data_filled$steps, data_filled$date, sum, na.rm=TRUE)
hist(total_steps, col = "green", 
     breaks = 20,
     main = "Total number of steps taken each day",
     xlab = "Number of steps per day")
mean(total_steps1,na.rm = TRUE)
median(total_steps1,na.rm = TRUE)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r }

data_filled$date <- as.Date(data_filled$date)
data_filled$weekday <- weekdays(data_filled$date)
data_filled$day_type<-ifelse(data_filled$weekday %in% c("Sunday","Saturday"), "Weekend","Weekday")

day_types_data <- aggregate(steps ~ interval + day_type, data=data_filled, mean)
ggplot(day_types_data, aes(interval, steps)) + 
        geom_line() + 
        facet_grid(day_type ~ .) +
        xlab("5-minute intervals") + 
        ylab("Avarage number of steps taken") +
        ggtitle("Weekdays and weekends activity patterns")

```